The Effects of Stellar Binarity on Transit Survey Occurrence Rates

### 2017-10-01 paper/ms.tex
paper: minor edits

Doing some algebra, and assuming $\gamma_R = q^\alpha$, this can be shown to be
\begin{align}
{\rm prob}(N_d) \propto N_d^{2/3} &\left(\frac{3}{4\pi 
	n_d}\right)^{5/3} d_{\rm max,s}^{-4} \ \nonumber\\
&\times \left[ 
	\left(\frac{3 N_d}{4\pi n_d}\right)^{2/3}  d_{\rm max,s}^{-2} - 1
 \right]^{\frac{1-\alpha}{\alpha} }
\end{align}
over the interval
\begin{equation}
N_d^{\rm lower} = \frac{4 \pi n_d}{3} (\sqrt{0.1^3 + 1} d_{\rm max,s})^3,
\end{equation}
\begin{equation}
N_d^{\rm upper} = \frac{4 \pi n_d}{3} (\sqrt{2}d_{\rm max,s})^3,
\end{equation}
and outside the stated interval ${\rm prob}(N_d) = 0$.

@@

The reason we derived all this is that we wanted to know the number of 
searchable binary stars.
The expected value for the number of double star systems in the sample is
\begin{equation}
\langle N_d \rangle = \int_{0}^{\infty} N_d\, {\rm prob}(N_d) \,{\rm d}N_d.
\end{equation}
Letting $\alpha=3.5$, this can be expressed as
\begin{equation}
\langle N_d \rangle \propto \mathcal{R}^{-3/2}
\int_{0.1^{7/2} + 1}^{2} u^{3/2} (u-1)^{5/7} \,{\rm d}u ,
\label{eq:integral_Nd}
\end{equation}
where non-dimensional constants are not shown, and $\mathcal{R}$ is defined as
\begin{equation}
\mathcal{R} \equiv \left(\frac{3}{4\pi n_d}\right)^{2/3} d_{\rm max,s}^{-2}.
\end{equation}
The integral in Eq.~\ref{eq:integral_Nd} has a closed-form solution in terms 
of the Gauss hypergeometric function, $_2F_1$. Once evaluated, and after 
normalizing ${\rm prob}(N_d)$, to 4 significant digits it gives
\begin{equation}
\langle N_d \rangle = 1.601 \left(\frac{4\pi n_d}{3}\right) d_{\rm max,s}^3.
\end{equation}
This gives the useful expression
\begin{align}
\frac{\langle N_d \rangle}{N_s} &= 1.601\, \frac{n_d}{n_s} \\
&= 1.601 \left(\frac{{\rm BF}}{1-{\rm BF}}\right).
\end{align}
Taking the sun-like star binary fraction of ${\rm BF} = 0.44$, this gives
$\langle N_d \rangle / N_s = 1.258$.
Compared to the binary-twin thought experiment of Sec.~\ref{sec:model_1}, in 
which the SNR-limited sample had $\approx 2.8$ times more binary systems than 
single systems, there are now $\approx 1.3$ times as many.
This is sensible, because the mean light ratio has decreased; it was 
previously 1, it is now $\langle \gamma_R \rangle \approx 0.27$.

>>>>

Doing some algebra, and assuming $\gamma_R = q^\alpha$, this can be shown to be
\begin{align}
{\rm prob}(N_d) \propto N_d^{2/3} &\left(\frac{3}{4\pi 
	n_d}\right)^{5/3} d_{\rm max,s}^{-5} \ \nonumber\\
&\times \left[ 
	\left(\frac{3 N_d}{4\pi n_d}\right)^{2/3}  d_{\rm max,s}^{-2} - 1
 \right]^{\frac{1-\alpha}{\alpha} }
\end{align}
over the interval
\begin{equation}
N_d^{\rm lower} = \frac{4 \pi n_d}{3} (\sqrt{0.1^3 + 1} d_{\rm max,s})^3,
\end{equation}
\begin{equation}
N_d^{\rm upper} = \frac{4 \pi n_d}{3} (\sqrt{2}d_{\rm max,s})^3,
\end{equation}
and outside the stated interval ${\rm prob}(N_d) = 0$.

@@

The reason we derived all this is that we wanted to know the number of 
searchable binary stars.
The expected value for the number of double star systems in the sample is
\begin{equation}
\langle N_d \rangle = \int_{0}^{\infty} N_d\, {\rm prob}(N_d) \,{\rm d}N_d.
\end{equation}
Letting $\alpha=3.5$, this can be expressed as
\begin{equation}
\langle N_d \rangle \propto \mathcal{R}^{-3/2}
\int_{0.1^{7/2} + 1}^{2} u^3 (u-1)^{-5/7} \,{\rm d}u ,
\label{eq:integral_Nd}
\end{equation}
where non-dimensional constants are not shown, and $\mathcal{R}$ is defined as
\begin{equation}
\mathcal{R} \equiv \left(\frac{3}{4\pi n_d}\right)^{2/3} d_{\rm max,s}^{-2}.
\end{equation}
The integral in Eq.~\ref{eq:integral_Nd} has a closed-form solution in terms 
of polynomials. Once evaluated, and after 
normalizing ${\rm prob}(N_d)$, to 4 significant digits it gives
\begin{equation}
\langle N_d \rangle = 1.590 \left(\frac{4\pi n_d}{3}\right) d_{\rm max,s}^3.
\end{equation}
This gives the useful expression
\begin{align}
\frac{\langle N_d \rangle}{N_s} &= 1.590\, \frac{n_d}{n_s} \\
&= 1.590 \left(\frac{{\rm BF}}{1-{\rm BF}}\right).
\end{align}
Taking the sun-like star binary fraction of ${\rm BF} = 0.44$, this gives
$\langle N_d \rangle / N_s = 1.25$.
Compared to the binary-twin thought experiment of Sec.~\ref{sec:model_1}, in 
which the SNR-limited sample had $\approx 2.8$ times more binary systems than 
single systems, there are now $\approx 1.25$ times as many.
This is sensible, because the mean light ratio has decreased; it was 
previously 1, it is now $\langle \gamma_R \rangle \approx 0.27$.
